\cvsection{Experience}
\begin{cventries}

%---------------------------------------------------------
\cventry
    {AbsInt Angewandte Informatik GmbH} % Organization
    {Software Engineer Intern} % Job title
    {Saarbr端cken, Germany} % Location
    {Sep. 2025 - Nov. 2025} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and implemented a pre-analysis module within RuleChecker to address the (theoretically undecidable) detection of persistent side effects in C++ code.}
            \item {Developed a top-down traversal of the Clang AST using a visitor-pattern approach to extract semantic information from program syntax.}
            \item {Produced a prototype capable of collecting useful data for supporting MISRA~C++ rule checking.}
            \item {Collaborated with the development team (approximately 20 people) through weekly meetings and technical discussions.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Istituto Omnicomprensivo Bonsignori} % Organization
    {Substitute Teacher} % Job title
    {Remedello, Italy} % Location
    {Mar. 2024 - Apr. 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Substitute teacher for a full position (18 hours) in Computer Science
            and Technology Laboratories at a technical high school (secondary level).}
            \item {Taught the following subjects: Tecnologie Informatiche (first biennium),
            Sistemi e Reti, Gestione di progetto e organizzazione di impresa,
            Tecnologie e Progettazione di Sistemi Informatici e Telecomunicazioni
            (second triennium).}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {University of Parma} % Organization
    {Intern (Curricular)} % Job title
    {Parma, Italy} % Location
    {Sep. 2022 - Mar. 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and implemented explainable machine learning methodologies
            in the context of source code similarity.}
            \item {Developed a graph representation based on Control-flow Graph and
            LLVM-IR generated by Clang, with subsequent feature generation through
            graph indexing tools.}
            \item {Performed similarity search using artificial intelligence techniques,
            including clustering and classification.}
            \item {Worked in a team of 4, and presented results at the 9th International
            Conference on Machine Learning, Optimization, and Data Science (LOD 2023).}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {University of Parma} % Organization
    {Research Fellow} % Job title
    {Parma, Italy} % Location
    {Jan. 2022 - Jul. 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Research theme: Implementation of parallel algorithms on GPU (transl.)}
            \item {Researched and implemented a new algorithm for NVIDIA GPUs (CUDA/C++)
            for computing eigenvalues and eigenvectors of small symmetric, positive
            semidefinite matrices.}
            \item {Studied and utilized Tensor Core architecture of NVIDIA GPUs for
            reimplementation of proprietary numerical computation algorithms.}
            \item {Implemented two ad-hoc solutions with CUDA/C++ to improve performance,
            achieving a speedup of x2N in execution time for matrix diagonalization.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {University of Parma} % Organization
    {Intern (Curricular)} % Job title
    {Parma, Italy} % Location
    {Jul. 2019 - Dec. 2019} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Studied and profiled C++ code for hydrodynamic simulation (dualSPHysics)
            using Intel速 compiler and Intel速 Parallel Studio suite.}
            \item {Optimized and parallelized part of the code with OpenMP API to leverage
            SIMD vector architecture of Intel速 processors.}
            \item {Achieved a 3x improvement in execution time for the parallelized
            solution.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Freelance/Small Group of People} % Organization
    {Web Developer} % Job title
    {Various Locations, Italy} % Location
    {2016 - 2021} % Date(s)
    {
            \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and implemented websites (showcase sites and small e-commerce)
            for acquaintances and local small businesses.}
            \item {Used technologies such as HTML, CSS, Javascript, PHP, SQL, Bootstrap
            framework, and Wordpress CMS.}
            \item {Managed web domains and hosting, and designed website structure and
            graphical interfaces.}
            \item {Created and managed small databases for the websites.}
            \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
